---
title: "log_reg_penguin data"
author: "Kelvin Nyongesa"
date: '2022-06-28'
output: html_document
---
### We will classify penguins using a simple logistics regression 
steps we will follow
1. load the data set
2. Clean the data
3.Train and test
4. create a model
5. Evaluate the model
##1. load the data
Lets get started by loading the libraries we will be using 

```{r}
library(tidyverse)
library(palmerpenguins)
penguins
```

###Lets ow do a simple visualize to see how our data set will look 
```{r}

  ggplot(penguins,aes(flipper_length_mm, bill_length_mm, color = sex, size = body_mass_g)) +
  geom_point(alpha = 0.5) +
  facet_wrap(~species)

```
##2. Clealing the data 
Given our model will use sex for classification we will drop the missing values. 
Then drop the data variables we might not in the classification
```{r}
penguins_df <- penguins %>%
  filter(!is.na(sex)) %>%
  select(-year, -island)
penguins_df
```
##3. Training and testing 
Here the sex variables been our stata is splited into traning and testing 
```{r}
library(tidymodels)

set.seed(123)
penguin_split <- initial_split(penguins_df, strata = sex)
penguin_train <- training(penguin_split)
penguin_test <- testing(penguin_split)
```
# we need to evaluate our model by checking on the trained data.
hence we will use bootstraps to help us evaluate
now let’s create bootstrap resamples of the training data, to evaluate our models.
```{r}
set.seed(123)
penguin_boot <- bootstraps(penguin_train)
penguin_boot
```
##4. Building the model
lets set our logistic regression model

```{r}
glm_spec <- logistic_reg() %>%
  set_engine("glm")

glm_spec
```
let’s start putting together a tidymodels workflow(), a helper object to help manage modeling pipelines with pieces that fit together.
```{r}
penguin_wf <- workflow() %>%
  add_formula(sex ~ .)

penguin_wf

```
Lets now add a model, and the fit to each of the resamples. First, we can fit the logistic regression model
```{r}
glm_rs <- penguin_wf %>%
  add_model(glm_spec) %>%
  fit_resamples(
    resamples = penguin_boot,
    control = control_resamples(save_pred = TRUE)
  )

glm_rs
```
##5. Evaluate the model
```{r}
collect_metrics(glm_rs)
```

###Now you have created your first working lOGISTIC REGRESSION MODEL